---
title: "Integrate female Garcia-Alonso with own dataset"
output:
  html_document:
    keep_md: true
    smart: false
    toc: true
    toc_float: true
    theme: united
date: 'Compiled: `r format(Sys.Date(), "%B %d, %Y")`'
---
***

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  cache.lazy = FALSE,
  tidy = TRUE
)
```

# J. Guo testis dataset
* 10.1016/j.stem.2020.12.004

## Libraries
```{r}
suppressMessages(library(plotly))
suppressMessages(library(Seurat))
suppressMessages(library(dplyr))
suppressMessages(library(Matrix))
suppressMessages(library(topGO))
suppressMessages(library(org.Hs.eg.db))
suppressMessages(library(gplots))
suppressMessages(library(genefilter))
suppressMessages(library(future))
suppressMessages(library(batchelor))
suppressMessages(library(SeuratWrappers))
suppressMessages(library(gprofiler2))
suppressMessages(library(ggplot2))
suppressMessages(library(gridExtra))

## We can use multiple cores for some functions, see: https://satijalab.org/seurat/v3.2/future_vignette.html
# plan("multiprocess", workers = 4)
# plan()
options(future.globals.maxSize= 6091289600)
outputDir = getwd()

# A list of cell cycle markers, from Tirosh et al, 2015, is loaded with Seurat.  We can
# segregate this list into markers of G2/M phase and markers of S phase
s.genes <- cc.genes$s.genes
g2m.genes <- cc.genes$g2m.genes
```

## Load Seurat objects
* Garcia AnnData was downloaded from: https://www.reproductivecellatlas.org/gonads.html
* Convetred using seuratDisk following: https://mojaveazure.github.io/seurat-disk/articles/convert-anndata.html
* Load own male dataset after filtering
```{r}
garcia_male <- readRDS("/path/to/human_main_female.rds")
own_female <- readRDS("/path/to/female_gonadal_remove_doublets_mnn.rds")
```


## Merge Seurat objects
* Add metadata own dataset
```{r}
own_female[["donor"]] <- "own"
own_female[["lineage"]] <- "own"
own_female[["dataset"]] <- "own"
garcia_male[["dataset"]] <- "garcia"

## Rename columns to match with own naming
colnames(garcia_male@meta.data)[1] <- "nFeature_RNA"
colnames(garcia_male@meta.data)[11] <- "percent.mt" ## Rename to align with own naming
colnames(garcia_male@meta.data)[12] <- "nCount_RNA"

gonads_mesonephros <- merge(x = garcia_male, 
                            y = own_female)
table(gonads_mesonephros[['donor']])
table(gonads_mesonephros[['age']])
gonads_mesonephros
```

## QC
* Visualize QC previously applied
```{r}
p1 <- VlnPlot(gonads_mesonephros, 
             features = "nFeature_RNA", 
             ncol = 1,
             pt.size = 0)
p1 <- p1 + geom_jitter(size = 0.1, alpha = 0.2) + ylim(0, NA) + theme(legend.position = "none")
p2 <- VlnPlot(gonads_mesonephros, 
             features = "nCount_RNA", 
             ncol = 1,
             pt.size = 0)
p2 <- p2 + geom_jitter(size = 0.1, alpha = 0.2) + ylim(0, NA) + theme(legend.position = "none")
p3 <- VlnPlot(gonads_mesonephros,
              features = "percent.mt",
              ncol = 1,
              pt.size = 0)
p3 <- p3 + geom_jitter(size = 0.1, alpha = 0.2) + ylim(0, NA) + theme(legend.position = "none")
grid.arrange(p1, p2, p3, ncol=3)
```

## Normalize and scale data
```{r}
gonads_mesonephros <- NormalizeData(gonads_mesonephros, 
                                    normalization.method = "LogNormalize", 
                                    scale.factor = 50000)
gonads_mesonephros <- FindVariableFeatures(gonads_mesonephros, 
                                           selection.method = "vst")
gonads_mesonephros <- ScaleData(gonads_mesonephros) 
```

## Run PCA, UMAP, clustering functions
```{r}
gonads_mesonephros <- RunPCA(gonads_mesonephros, 
                             verbose = FALSE)
ElbowPlot(gonads_mesonephros)
gonads_mesonephros <- FindNeighbors(gonads_mesonephros, 
                                    dims = c(1:15))
gonads_mesonephros <- FindClusters(gonads_mesonephros,
                                   resolution = 0.4)
gonads_mesonephros <- RunUMAP(gonads_mesonephros, 
                              dims = c(1:15))
DimPlot(gonads_mesonephros, 
        reduction = "umap")
ggsave("umap_clusters.pdf",
       width = 10,
       height = 7)
DimPlot(gonads_mesonephros, 
        reduction = "umap",
        group.by = "lineage")
ggsave("umap_clusters_age.pdf",
       width = 10,
       height = 7)
DimPlot(gonads_mesonephros, 
        reduction = "umap",
        group.by = "donor")
ggsave("umap_clusters_origin.pdf",
       width = 10,
       height = 7)
saveRDS(object = gonads_mesonephros, 
        file = "gonads_mesonephros_no_mnn.rds")
```

## Batch corrrect MNN between in garcia and own
* We use the "donor" field, which will also correct for the donors present inthe garcia
* Our own dataset will be treated as another donor 
```{r}
gonads_mesonephros <- RunFastMNN(object.list = SplitObject(gonads_mesonephros, split.by = "donor"))
```

## Redo with mnn correction
```{r}
gonads_mesonephros <- FindNeighbors(gonads_mesonephros, 
                                    reduction = "mnn",
                                    dims = c(1:15))
gonads_mesonephros <- FindClusters(gonads_mesonephros,
                                   resolution = 0.4)
gonads_mesonephros <- RunUMAP(gonads_mesonephros,
                              reduction = "mnn",
                              dims = c(1:15))
DimPlot(gonads_mesonephros, 
        reduction = "umap")
ggsave("umap_clusters_mnn.pdf",
       width = 10,
       height = 7)
DimPlot(gonads_mesonephros, 
        reduction = "umap",
        group.by = "lineage")
ggsave("umap_clusters_age_mnn.pdf",
       width = 10,
       height = 7)
DimPlot(gonads_mesonephros, 
        reduction = "umap",
        group.by = "donor")
ggsave("umap_clusters_origin_mnn.pdf",
       width = 10,
       height = 7)
saveRDS(object = gonads_mesonephros, 
        file = "gonads_mesonephros_mnn.rds")
```

### Session Info
```{r}
sessionInfo()
```
